---
title: "linear models"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse) 
library(broom)
library(p8105.datasets)

set.seed(1)

```

look at AIrbnb data....
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group,
         neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit a model for price as an outcome
```{r}
fit =lm(price ~ stars + boro, data = nyc_airbnb)
```

look at the summaies
```{r}
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
```

look at better summaries
```{r}
broom::tidy(fit)

fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)


fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^boro", "Boro: "),
         signif = ifelse(p.value < 0.05, "*", "")) %>% 
  knitr::kable(digits = 3)
```


look at other summaries
```{r}
fit %>% 
  broom::glance() %>% 
  select(r.squared, adj.r.squared)
```

be careful with factors....


nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(boro = fct_infreq(boro),
         room_type = fct_infreq(room_type)) %>% 
  
  fit = lm(price ~ stars+boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()



### diagnostics

```{r}

nyc_airbnb %>%     
modelr::add_residuals(fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_violin()

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()


nyc_airbnb %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = stars, y = pred, color = boro)) + geom_point()
```

### hypothesis test

```{r}
fit %>% 
  broom::tidy()
```

compare nested models
```{r}
fit_null = lm(price~ stars+boro, data = nyc_airbnb)
fit_alt = lm(price ~stars+boro+room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

###nested data
```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Nesting and then fitting
```{r}
nest_lm_res =
  nyc_airbnb %>% 
  group_by(boro) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

```{r}
nest_lm_res %>% 
  select(boro, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  spread(key = term, value = estimate) %>% 
  knitr::kable(digits = 3)
```

more example...
```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  group_by(neighborhood) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

View some results...
```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate))+geom_point()+facet_grid(~term)+
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

